### 2022-03-22 paper/output/document/appendix.tex
finished another read thrgh

%
\begin{isabellebody}%
\setisabellecontext{appendix}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Alternate Definitions of a Maxim \label{maximmotive}%
}
\isamarkuptrue%
%
\isamarkupsubsection{Korsgaard's Act-Goal View%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I adopt O'Niell's definition of a maxim, which builds on Korsgaard's weaker interpretation of 
a maxim as an act, goal pair. She interprets Kant's example meanings as having the form ``to-do-this-act-for-
the-sake-of-this-end,'' which could be formalized as a pair of an act and goal \citep{actingforareason}.
For example, under this view, one example maxim might be, ``Falsely promise to repay a loan in order
to get some easy cash.''

O'Niell's view only differs from this view in the inclusion of the circumstances
on which the agent acts. This inclusion creates a representation of a maxim that is strictly more expressive than 
Korsgaard's interpretation; every (circumstance, act, goal) tuple can be represented as an (act, goal) pair
by simply dropping the circumstances, but the same (act, goal) pair could correspond to many different
(circumstance, act, goal) tuples, all with varying moral statuses. Because my representation of a maxim
is more expressive than Korsgaard's, my results are stronger than those that would be achieved with 
Korsgaard's view. Thus, proponents of Korsgaard's view could simply ignore the circumstances in my
representation of a maxim and still achieve their desired results.

One issue with Korsgaard's view is that an actionable maxim will necessarily
require some circumstances built-in because the agent will need to know when to act on the maxim. For example,
the falsely promising maxim bakes in the circumstances that the actor has access to lender, needs money, 
and that the lender will expect their money back. At an even more granular level, this maxim implicitly includes
a definition of a lender and of falsely promising, both of which are circumstantial. Given that all
maxims necessarily include some circumstances, O'Niell's view makes these implicit circumstances
explicit. This precision is a benefit; so long as my circumstances are not so finely grained that they
are uninterpretable, they render O'Niell's maxims more precise than Korsgaard's maxims.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kitcher's View on Motives%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kitcher begins with O'Niell's 
circumstance, act, goal view and expands it to include the motive for a maxim \citep{whatisamaxim}. 
This additional component is read as ``In circumstance C, I will do A in order to G because of M,'' 
where M may be ``duty'' or ``self-love.'' Kitcher argues that the inclusion of motive is necessary 
for the fullest, most general form of a maxim in order to capture Kant's idea that an action derives 
its moral worth from being done for the sake of duty itself. Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C.'' In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

@@

%:%28=8%:%
%:%40=10%:%
%:%41=11%:%
%:%42=12%:%
%:%43=13%:%
%:%44=14%:%
%:%45=15%:%
%:%46=16%:%
%:%47=17%:%
%:%48=18%:%
%:%49=19%:%
%:%50=20%:%
%:%51=21%:%
%:%52=22%:%
%:%53=23%:%
%:%54=24%:%
%:%55=25%:%
%:%56=26%:%
%:%57=27%:%
%:%58=28%:%
%:%59=29%:%
%:%60=30%:%
%:%61=31%:%
%:%62=32%:%
%:%71=35%:%
%:%83=37%:%
%:%84=38%:%
%:%85=39%:%
%:%86=40%:%
%:%87=41%:%
%:%88=42%:%
%:%89=43%:%
%:%90=44%:%
%:%91=45%:%
%:%92=46%:%
%:%93=47%:%
%:%94=48%:%
%:%95=49%:%
%:%96=50%:%
%:%97=51%:%
%:%98=52%:%
%:%99=53%:%
%:%100=54%:%
%:%101=55%:%
%:%102=56%:%
%:%103=57%:%
%:%104=58%:%
%:%105=59%:%
%:%106=60%:%
%:%107=61%:%
%:%108=62%:%
%:%117=65%:%
%:%129=67%:%
%:%130=68%:%
%:%131=69%:%
%:%132=70%:%
%:%133=71%:%
%:%142=73%:%
%:%154=75%:%
%:%155=76%:%
%:%156=77%:%
%:%158=79%:%
%:%159=79%:%
%:%160=79%:%
%:%163=81%:%
%:%164=82%:%
%:%165=83%:%
%:%166=84%:%
%:%167=85%:%
%:%168=86%:%
%:%170=88%:%
%:%171=88%:%
%:%173=89%:%
%:%174=89%:%
%:%176=90%:%
%:%177=91%:%
%:%180=93%:%
%:%181=94%:%
%:%182=95%:%
%:%183=96%:%
%:%185=98%:%
%:%186=98%:%
%:%187=99%:%
%:%188=100%:%
%:%189=100%:%
%:%190=101%:%
%:%191=102%:%
%:%192=102%:%
%:%193=103%:%
%:%194=104%:%
%:%195=104%:%
%:%196=105%:%
%:%198=107%:%
%:%199=108%:%
%:%200=109%:%
%:%202=111%:%
%:%203=111%:%
%:%204=112%:%
%:%205=113%:%
%:%206=113%:%
%:%207=114%:%
%:%209=116%:%
%:%213=118%:%
%:%214=119%:%
%:%215=120%:%
%:%216=121%:%
%:%217=122%:%
%:%218=123%:%
%:%219=124%:%
%:%223=126%:%
%:%224=127%:%
%:%225=128%:%
%:%226=129%:%
%:%227=130%:%
%:%228=131%:%
%:%229=132%:%
%:%231=134%:%
%:%232=134%:%
%:%233=135%:%
%:%234=136%:%
%:%235=137%:%
%:%236=137%:%
%:%238=137%:%
%:%242=137%:%
%:%243=137%:%
%:%245=138%:%
%:%246=139%:%
%:%247=140%:%
%:%248=141%:%
%:%258=143%:%
%:%259=144%:%
%:%260=145%:%
%:%261=146%:%
%:%262=147%:%
%:%263=148%:%
%:%264=149%:%
%:%265=150%:%
%:%266=151%:%
%:%267=152%:%
%:%269=154%:%
%:%270=154%:%
%:%271=155%:%
%:%272=156%:%
%:%273=157%:%
%:%274=157%:%
%:%276=157%:%
%:%280=157%:%
%:%281=157%:%
%:%283=158%:%
%:%284=159%:%
%:%285=160%:%
%:%286=161%:%
%:%296=163%:%
%:%297=164%:%
%:%298=165%:%
%:%299=166%:%
%:%300=167%:%
%:%301=168%:%
%:%302=169%:%
%:%303=170%:%
%:%304=171%:%
%:%306=173%:%
%:%307=173%:%
%:%308=174%:%
%:%309=175%:%
%:%310=176%:%
%:%311=176%:%
%:%313=176%:%
%:%317=176%:%
%:%318=176%:%
%:%320=177%:%
%:%321=178%:%
%:%322=179%:%
%:%323=180%:%
%:%333=182%:%
%:%334=183%:%
%:%351=208%:%
%:%355=210%:%
%:%356=211%:%
%:%357=212%:%
%:%358=213%:%
%:%359=214%:%
%:%361=217%:%
%:%362=217%:%
%:%364=218%:%
%:%365=219%:%
%:%366=220%:%
%:%369=222%:%
%:%370=223%:%
%:%372=225%:%
%:%373=225%:%
%:%374=226%:%
%:%375=227%:%
%:%376=227%:%
%:%378=227%:%
%:%382=227%:%
%:%383=227%:%
%:%385=228%:%
%:%386=229%:%
%:%387=230%:%
%:%388=231%:%
%:%389=232%:%
%:%390=233%:%
%:%391=234%:%
%:%392=235%:%
%:%400=235%:%
%:%401=236%:%
%:%402=237%:%
%:%403=237%:%
%:%405=239%:%
%:%406=240%:%
%:%408=242%:%
%:%409=242%:%
%:%410=242%:%
%:%412=242%:%
%:%416=242%:%
%:%417=242%:%
%:%419=243%:%
%:%420=244%:%
%:%421=245%:%
%:%422=246%:%
%:%432=248%:%
%:%433=249%:%
%:%434=250%:%
%:%435=251%:%
%:%444=253%:%
%:%456=255%:%
%:%457=256%:%
%:%458=257%:%
%:%459=258%:%
%:%460=259%:%
%:%461=260%:%
%:%462=261%:%
%:%463=262%:%
%:%464=263%:%
%:%465=264%:%
%:%466=265%:%
%:%468=267%:%
%:%469=267%:%
%:%470=268%:%
%:%471=269%:%
%:%472=269%:%
%:%474=269%:%
%:%478=269%:%
%:%488=271%:%

@@

%:%492=275%:%
%:%493=275%:%
%:%494=276%:%
%:%495=277%:%
%:%496=278%:%
%:%497=278%:%
%:%499=278%:%
%:%503=278%:%
%:%504=278%:%
%:%506=279%:%
%:%507=280%:%
%:%508=281%:%
%:%509=282%:%
%:%519=284%:%
%:%520=285%:%
%:%522=287%:%
%:%523=287%:%
%:%524=288%:%
%:%525=289%:%
%:%526=290%:%
%:%527=291%:%
%:%528=291%:%
%:%530=291%:%
%:%534=291%:%
%:%535=291%:%
%:%537=292%:%
%:%538=293%:%
%:%539=294%:%
%:%540=295%:%
%:%541=296%:%
%:%542=297%:%
%:%552=299%:%
%:%553=300%:%
%:%554=301%:%
%:%556=303%:%
%:%557=303%:%
%:%558=304%:%
%:%559=305%:%
%:%560=306%:%
%:%561=306%:%
%:%563=306%:%
%:%567=306%:%
%:%568=306%:%
%:%570=307%:%
%:%571=308%:%
%:%572=309%:%
%:%573=310%:%
%:%574=311%:%
%:%584=314%:%
%:%585=315%:%
%:%586=316%:%
%:%587=317%:%
%:%588=318%:%
%:%589=319%:%
%:%590=320%:%
%:%592=322%:%
%:%593=322%:%
%:%595=323%:%
%:%596=324%:%
%:%597=325%:%
%:%598=325%:%
%:%599=326%:%
%:%600=327%:%
%:%601=327%:%
%:%603=328%:%
%:%604=328%:%
%:%606=329%:%
%:%607=330%:%
%:%608=330%:%
%:%609=331%:%
%:%610=332%:%
%:%611=332%:%
%:%613=333%:%
%:%614=334%:%
%:%617=336%:%
%:%618=337%:%
%:%620=339%:%
%:%621=339%:%
%:%622=340%:%
%:%623=341%:%
%:%624=341%:%
%:%626=341%:%
%:%630=341%:%
%:%631=341%:%
%:%633=342%:%
%:%634=343%:%
%:%635=344%:%
%:%636=345%:%
%:%637=346%:%
%:%638=347%:%
%:%639=348%:%
%:%649=350%:%
%:%650=351%:%
%:%651=352%:%
%:%652=353%:%
%:%653=354%:%
%:%657=356%:%
%:%658=357%:%
%:%659=358%:%
%:%660=359%:%
%:%661=360%:%
%:%662=361%:%
%:%666=363%:%
%:%667=364%:%
%:%668=365%:%
%:%670=367%:%
%:%671=367%:%
%:%672=368%:%
%:%675=369%:%
%:%679=369%:%
%:%680=369%:%
%:%682=370%:%

@@

%:%691=371%:%
%:%692=372%:%
%:%693=372%:%
%:%694=373%:%

@@

%:%696=375%:%
%:%697=375%:%
%:%699=375%:%
%:%703=375%:%
%:%704=375%:%
%:%706=376%:%
%:%707=377%:%
%:%708=378%:%
%:%709=379%:%
%:%710=380%:%
%:%720=382%:%
%:%721=383%:%
%:%722=384%:%
%:%723=385%:%
%:%724=386%:%
%:%725=387%:%
%:%726=388%:%
%:%727=389%:%
%:%728=390%:%
%:%729=391%:%
%:%730=392%:%
%:%731=393%:%
%:%732=394%:%
%:%733=395%:%
%:%734=396%:%
%:%735=397%:%
%:%736=398%:%
%:%737=399%:%
%:%738=400%:%
%:%739=401%:%
%:%740=402%:%
%:%741=403%:%
%:%745=405%:%
%:%746=406%:%
%:%747=407%:%
%:%748=408%:%
%:%749=409%:%
%:%750=410%:%
%:%751=411%:%
%:%752=412%:%
%:%753=413%:%
%:%757=416%:%
%:%758=417%:%
%:%759=418%:%
%:%760=419%:%
%:%762=421%:%
%:%763=421%:%
%:%764=422%:%
%:%765=423%:%
%:%766=423%:%
%:%767=424%:%
%:%770=425%:%
%:%774=425%:%
%:%775=425%:%
%:%776=425%:%
%:%778=426%:%
%:%779=427%:%
%:%789=429%:%

@@

%:%791=431%:%
%:%792=432%:%
%:%793=433%:%
%:%794=434%:%
%:%795=435%:%
%:%796=436%:%
%:%797=437%:%
%:%798=438%:%
%:%799=439%:%
%:%800=440%:%
%:%801=441%:%
%:%802=442%:%
%:%803=443%:%
%:%804=444%:%
%:%805=445%:%
%:%806=446%:%
%:%807=447%:%
%:%808=448%:%
%:%809=449%:%
%:%810=450%:%
%:%811=451%:%
%:%812=452%:%
%:%813=453%:%
%:%814=454%:%
%:%815=455%:%
%:%817=457%:%
%:%818=457%:%
%:%819=458%:%
%:%820=459%:%
%:%821=460%:%
%:%822=460%:%
%:%824=460%:%
%:%828=460%:%
%:%829=460%:%
%:%831=461%:%
%:%832=462%:%
%:%833=463%:%
%:%834=464%:%
%:%835=465%:%
%:%836=466%:%
%:%837=467%:%
%:%838=468%:%
%:%848=470%:%
%:%849=471%:%
%:%850=472%:%
%:%851=473%:%
%:%852=474%:%
%:%853=475%:%
%:%854=476%:%

>>>>

%
\begin{isabellebody}%
\setisabellecontext{appendix}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Alternate Definitions of a Maxim \label{maximmotive}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In Section \ref{whatisamaxim}, I explain and justify O'Neill's definition of a maxim as a circumstance,
act, goal triple. In this appendix, I explore two alternate definitions of maxim: Korsgaard's definition, 
which is weaker than O'Neill's, and Kitcher's definition, which is stronger than O'Neill's. I argue that 
O'Neill's definition offers the right amount of strength for my project.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Korsgaard's Act-Goal View%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
I adopt O'Neill's definition of a maxim, which builds on Korsgaard's weaker interpretation of 
a maxim as an act, goal pair. Korsgaard interprets Kant's example meanings as having the form ``to-do-this-act-for-
the-sake-of-this-end,'' which could be formalized as a pair of an act and goal \citep{actingforareason}.
Under this view, one example maxim might be, ``Falsely promise to repay a loan in order
to get some easy cash.''

O'Neill's view only differs from this view in the inclusion of the circumstances
under which the agent acts. This inclusion creates a representation of a maxim that is strictly more expressive than 
Korsgaard's interpretation; every circumstance, act, goal triple can be represented as an act, goal pair
by simply dropping the circumstances, but the same act, goal pair could correspond to many different
circumstance, act, goal triples, all with varying moral statuses. Because my representation of a maxim
is more expressive than Korsgaard's, my results are stronger than those that would be achieved with 
Korsgaard's view. Thus, proponents of Korsgaard's view could simply ignore the circumstances in my
representation of a maxim and still achieve their desired results.

One issue with Korsgaard's view is that an actionable maxim will necessarily
require some circumstances built-in because the agent will need to know when to act on the maxim. For example,
the falsely promising maxim bakes in the circumstances that the actor has access to lender, needs money, 
and that the lender will expect their money back. At an even more granular level, this maxim implicitly includes
a definition of a lender and of falsely promising, both of which are circumstantial. All
maxims necessarily include some circumstances and  O'Neill's view makes these implicit circumstances
explicit. This precision is a benefit; so long as my circumstances are not so finely grained that they
are uninterpretable, they render O'Neill's maxims more precise than Korsgaard's maxims.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Kitcher's View Including Motives%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Kitcher begins with O'Neill's 
circumstance, act, goal view and expands it to include the motive for a maxim \citep{whatisamaxim}. 
This additional component is read as ``In circumstance C, I will do A in order to G because of M,'' 
where M may be ``duty'' or ``self-love.'' Kitcher argues that the inclusion of motive is necessary 
for the fullest, most general form of a maxim in order to capture Kant's idea that an action derives 
its moral worth from being done for the sake of duty itself. Under this view, the FUL would obligate maxims of the form 
``In circumstance C, I will do A in order to G because I can will that I and everyone else simultaneously
will do A in order to G in circumstance C.'' In other words, if Kant is correct in arguing that moral 
actions must be done from the motive of duty, the affirmative result of the FUL becomes 
the motive for a moral action.

@@

%:%36=8%:%
%:%37=9%:%
%:%38=10%:%
%:%39=11%:%
%:%48=13%:%
%:%60=15%:%
%:%61=16%:%
%:%62=17%:%
%:%63=18%:%
%:%64=19%:%
%:%65=20%:%
%:%66=21%:%
%:%67=22%:%
%:%68=23%:%
%:%69=24%:%
%:%70=25%:%
%:%71=26%:%
%:%72=27%:%
%:%73=28%:%
%:%74=29%:%
%:%75=30%:%
%:%76=31%:%
%:%77=32%:%
%:%78=33%:%
%:%79=34%:%
%:%80=35%:%
%:%81=36%:%
%:%82=37%:%
%:%91=40%:%
%:%103=42%:%
%:%104=43%:%
%:%105=44%:%
%:%106=45%:%
%:%107=46%:%
%:%108=47%:%
%:%109=48%:%
%:%110=49%:%
%:%111=50%:%
%:%112=51%:%
%:%113=52%:%
%:%114=53%:%
%:%115=54%:%
%:%116=55%:%
%:%117=56%:%
%:%118=57%:%
%:%119=58%:%
%:%120=59%:%
%:%121=60%:%
%:%122=61%:%
%:%123=62%:%
%:%124=63%:%
%:%125=64%:%
%:%126=65%:%
%:%127=66%:%
%:%128=67%:%
%:%137=70%:%
%:%149=72%:%
%:%150=73%:%
%:%151=74%:%
%:%152=75%:%
%:%153=76%:%
%:%162=78%:%
%:%174=80%:%
%:%175=81%:%
%:%176=82%:%
%:%178=84%:%
%:%179=84%:%
%:%180=84%:%
%:%183=86%:%
%:%184=87%:%
%:%185=88%:%
%:%186=89%:%
%:%187=90%:%
%:%188=91%:%
%:%190=93%:%
%:%191=93%:%
%:%193=94%:%
%:%194=94%:%
%:%196=95%:%
%:%197=96%:%
%:%200=98%:%
%:%201=99%:%
%:%202=100%:%
%:%203=101%:%
%:%205=103%:%
%:%206=103%:%
%:%207=104%:%
%:%208=105%:%
%:%209=105%:%
%:%210=106%:%
%:%211=107%:%
%:%212=107%:%
%:%213=108%:%
%:%214=109%:%
%:%215=109%:%
%:%216=110%:%
%:%218=112%:%
%:%219=113%:%
%:%220=114%:%
%:%222=116%:%
%:%223=116%:%
%:%224=117%:%
%:%225=118%:%
%:%226=118%:%
%:%227=119%:%
%:%229=121%:%
%:%233=123%:%
%:%234=124%:%
%:%235=125%:%
%:%236=126%:%
%:%237=127%:%
%:%238=128%:%
%:%239=129%:%
%:%243=131%:%
%:%244=132%:%
%:%245=133%:%
%:%246=134%:%
%:%247=135%:%
%:%248=136%:%
%:%249=137%:%
%:%251=139%:%
%:%252=139%:%
%:%253=140%:%
%:%254=141%:%
%:%255=142%:%
%:%256=142%:%
%:%258=142%:%
%:%262=142%:%
%:%263=142%:%
%:%265=143%:%
%:%266=144%:%
%:%267=145%:%
%:%268=146%:%
%:%278=148%:%
%:%279=149%:%
%:%280=150%:%
%:%281=151%:%
%:%282=152%:%
%:%283=153%:%
%:%284=154%:%
%:%285=155%:%
%:%286=156%:%
%:%287=157%:%
%:%289=159%:%
%:%290=159%:%
%:%291=160%:%
%:%292=161%:%
%:%293=162%:%
%:%294=162%:%
%:%296=162%:%
%:%300=162%:%
%:%301=162%:%
%:%303=163%:%
%:%304=164%:%
%:%305=165%:%
%:%306=166%:%
%:%316=168%:%
%:%317=169%:%
%:%318=170%:%
%:%319=171%:%
%:%320=172%:%
%:%321=173%:%
%:%322=174%:%
%:%323=175%:%
%:%324=176%:%
%:%326=178%:%
%:%327=178%:%
%:%328=179%:%
%:%329=180%:%
%:%330=181%:%
%:%331=181%:%
%:%333=181%:%
%:%337=181%:%
%:%338=181%:%
%:%340=182%:%
%:%341=183%:%
%:%342=184%:%
%:%343=185%:%
%:%353=187%:%
%:%354=188%:%
%:%371=213%:%
%:%375=215%:%
%:%376=216%:%
%:%377=217%:%
%:%378=218%:%
%:%379=219%:%
%:%381=222%:%
%:%382=222%:%
%:%384=223%:%
%:%385=224%:%
%:%386=225%:%
%:%389=227%:%
%:%390=228%:%
%:%392=230%:%
%:%393=230%:%
%:%394=231%:%
%:%395=232%:%
%:%396=232%:%
%:%398=232%:%
%:%402=232%:%
%:%403=232%:%
%:%405=233%:%
%:%406=234%:%
%:%407=235%:%
%:%408=236%:%
%:%409=237%:%
%:%410=238%:%
%:%411=239%:%
%:%412=240%:%
%:%420=240%:%
%:%421=241%:%
%:%422=242%:%
%:%423=242%:%
%:%425=244%:%
%:%426=245%:%
%:%428=247%:%
%:%429=247%:%
%:%430=247%:%
%:%432=247%:%
%:%436=247%:%
%:%437=247%:%
%:%439=248%:%
%:%440=249%:%
%:%441=250%:%
%:%442=251%:%
%:%452=253%:%
%:%453=254%:%
%:%454=255%:%
%:%455=256%:%
%:%464=258%:%
%:%476=260%:%
%:%477=261%:%
%:%478=262%:%
%:%479=263%:%
%:%480=264%:%
%:%481=265%:%
%:%482=266%:%
%:%483=267%:%
%:%484=268%:%
%:%485=269%:%
%:%486=270%:%
%:%488=272%:%

@@

%:%491=274%:%
%:%492=274%:%
%:%494=274%:%
%:%498=274%:%
%:%508=276%:%
%:%509=277%:%
%:%510=278%:%
%:%512=280%:%
%:%513=280%:%
%:%514=281%:%
%:%515=282%:%
%:%516=283%:%
%:%517=283%:%
%:%519=283%:%
%:%523=283%:%
%:%524=283%:%
%:%526=284%:%
%:%527=285%:%
%:%528=286%:%
%:%529=287%:%
%:%539=289%:%
%:%540=290%:%
%:%542=292%:%
%:%543=292%:%
%:%544=293%:%
%:%545=294%:%
%:%546=295%:%
%:%547=296%:%
%:%548=296%:%
%:%550=296%:%
%:%554=296%:%
%:%555=296%:%
%:%557=297%:%
%:%558=298%:%
%:%559=299%:%
%:%560=300%:%
%:%561=301%:%
%:%562=302%:%
%:%572=304%:%
%:%573=305%:%
%:%574=306%:%
%:%576=308%:%
%:%577=308%:%
%:%578=309%:%
%:%579=310%:%
%:%580=311%:%
%:%581=311%:%
%:%583=311%:%
%:%587=311%:%
%:%588=311%:%
%:%590=312%:%
%:%591=313%:%
%:%592=314%:%
%:%593=315%:%
%:%594=316%:%
%:%604=319%:%
%:%605=320%:%
%:%606=321%:%
%:%607=322%:%
%:%608=323%:%
%:%609=324%:%
%:%610=325%:%
%:%612=327%:%
%:%613=327%:%
%:%615=328%:%
%:%616=329%:%
%:%617=330%:%
%:%618=330%:%
%:%619=331%:%
%:%620=332%:%
%:%621=332%:%
%:%623=333%:%
%:%624=333%:%
%:%626=334%:%
%:%627=335%:%
%:%628=335%:%
%:%629=336%:%
%:%630=337%:%
%:%631=337%:%
%:%633=338%:%
%:%634=339%:%
%:%637=341%:%
%:%638=342%:%
%:%640=344%:%
%:%641=344%:%
%:%642=345%:%
%:%643=346%:%
%:%644=346%:%
%:%646=346%:%
%:%650=346%:%
%:%651=346%:%
%:%653=347%:%
%:%654=348%:%
%:%655=349%:%
%:%656=350%:%
%:%657=351%:%
%:%658=352%:%
%:%659=353%:%
%:%669=355%:%
%:%670=356%:%
%:%671=357%:%
%:%672=358%:%
%:%673=359%:%
%:%677=361%:%
%:%678=362%:%
%:%679=363%:%
%:%680=364%:%
%:%681=365%:%
%:%682=366%:%
%:%686=368%:%
%:%687=369%:%

@@

%:%690=372%:%
%:%691=372%:%
%:%692=373%:%

@@

%:%699=374%:%
%:%700=374%:%
%:%702=375%:%
%:%708=375%:%
%:%711=376%:%
%:%712=377%:%
%:%713=377%:%
%:%714=378%:%
%:%715=379%:%
%:%716=380%:%
%:%717=380%:%
%:%719=380%:%
%:%723=380%:%
%:%724=380%:%
%:%726=381%:%
%:%727=382%:%
%:%728=383%:%
%:%729=384%:%
%:%730=385%:%
%:%740=387%:%
%:%741=388%:%
%:%742=389%:%
%:%743=390%:%
%:%744=391%:%
%:%745=392%:%
%:%746=393%:%
%:%747=394%:%
%:%748=395%:%
%:%749=396%:%
%:%750=397%:%
%:%751=398%:%
%:%752=399%:%
%:%753=400%:%
%:%754=401%:%
%:%755=402%:%
%:%756=403%:%
%:%757=404%:%
%:%758=405%:%
%:%759=406%:%
%:%760=407%:%
%:%761=408%:%
%:%765=410%:%
%:%766=411%:%
%:%767=412%:%
%:%768=413%:%
%:%769=414%:%
%:%770=415%:%
%:%771=416%:%
%:%772=417%:%
%:%773=418%:%
%:%777=421%:%
%:%778=422%:%
%:%779=423%:%
%:%780=424%:%
%:%782=426%:%
%:%783=426%:%
%:%784=427%:%
%:%785=428%:%
%:%786=428%:%
%:%787=429%:%

@@

%:%794=430%:%
%:%795=430%:%
%:%796=430%:%
%:%798=431%:%
%:%799=432%:%
%:%809=434%:%
%:%810=435%:%
%:%811=436%:%
%:%812=437%:%
%:%813=438%:%
%:%814=439%:%
%:%815=440%:%
%:%816=441%:%
%:%817=442%:%
%:%818=443%:%
%:%819=444%:%
%:%820=445%:%
%:%821=446%:%
%:%822=447%:%
%:%823=448%:%
%:%824=449%:%
%:%825=450%:%
%:%826=451%:%
%:%827=452%:%
%:%828=453%:%
%:%829=454%:%
%:%830=455%:%
%:%831=456%:%
%:%832=457%:%
%:%833=458%:%
%:%834=459%:%
%:%835=460%:%
%:%837=462%:%
%:%838=462%:%
%:%839=463%:%
%:%840=464%:%
%:%841=465%:%
%:%842=465%:%
%:%844=465%:%
%:%848=465%:%
%:%849=465%:%
%:%851=466%:%
%:%852=467%:%
%:%853=468%:%
%:%854=469%:%
%:%855=470%:%
%:%856=471%:%
%:%857=472%:%
%:%858=473%:%
%:%868=475%:%
%:%869=476%:%
%:%870=477%:%
%:%871=478%:%
%:%872=479%:%
%:%873=480%:%
%:%874=481%:%
